---
title: "Comparing Hector integrated vs non integrated DOECLIM"
output:
  html_notebook:
    toc: yes
    toc_depth: '4'
    toc_float: yes
    number_sections: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Set Up 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE)
# see https://bookdown.org/yihui/rmarkdown-cookbook/ for more info on markdowns
```

```{r}
library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)

BASE_DIR <- here::here()

theme_set(theme_bw())


data <- rbind(read.csv("~/Desktop/hector_doeclim.csv", stringsAsFactors = FALSE), 
              read.csv("~/Desktop/hector_land-tracking.csv", stringsAsFactors = FALSE)) %>%  
    dplyr::filter(grepl(pattern = "ssp", x = scenario))
```

## Objective 

How much does Hector output change by when DOECLIM is integrated vs. fully integrated. 

# Compare Hector Outputs

## Temperature 

```{r}
data %>% 
    dplyr::filter(variable %in% c("Tgav", "Tgav_land", "Tgav_ocean_air", "Tgav_ocean_ST")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```


```{r}
data %>% 
    dplyr::filter(variable %in% c("Temp_HL", "Temp_LL")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```

Not surprising that we see a large change here since we are swtiching from tas to tos data so the fact that the HL and LL temp is now lower is not surprising. 


## Carbon Fluxes 

```{r}
data %>% 
    dplyr::filter(variable %in% c("atm_ocean_flux", "atm_ocean_flux_LL", "atm_ocean_flux_HL")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```


## Ocean Vars 

```{r}
data %>% 
    dplyr::filter(variable %in% c("pH_HL", "pH_LL", "CO3_HL", "CO3_LL", "PCO2_HL", "PCO2_LL")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```

```{r}
data %>% 
    dplyr::filter(variable %in% c("carbon_HL", "carbon_LL", "carbon_IO", "carbon_DO")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```

## Terrestiral Carbon 

```{r}
data %>% 
    dplyr::filter(variable %in% c("npp")) %>% 
    ggplot(aes(year, value, color = version, linetype = version, groupby = interaction(variable, version, scenario))) + 
    geom_line() + 
    facet_wrap("variable", scales = "free") + 
    theme_bw() + 
    theme(legend.position = "bottom") + 
    labs(y = NULL, x = NULL)
```

# Percent Difference 

```{r}
data %>% 
    tidyr::spread(version, value) %>% 
    dplyr::mutate(percent = 100 * (`full doeclim integration` - `land-tracking`)/ `land-tracking`) -> 
    percent_change_data 

percent_change_data %>% 
    dplyr::group_by(variable, scenario) %>%  
    dplyr::summarise(value = mean(percent)) %>% 
    tidyr::spread(scenario, value) %>% 
    knitr::kable(digits = 3, caption = "(doeclim - land tracking) / land tracking")
```

## Temperature

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("Tgav", "Tgav_land", "Tgav_ocean_air", "Tgav_ocean_ST")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    coord_cartesian(ylim = c(-50, 50)) + 
    facet_wrap("variable") + 
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("Temp_HL", "Temp_LL")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    facet_wrap("variable") + 
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```

## Carbon Fluxes

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("atm_ocean_flux", "atm_ocean_flux_LL", "atm_ocean_flux_HL")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    facet_wrap("variable") + 
    coord_cartesian(ylim = c(-75, 75)) +
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```

## Ocean Vars

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("pH_HL", "pH_LL", "CO3_HL",
                                  "CO3_LL", "PCO2_HL", "PCO2_LL")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    facet_wrap("variable") + 
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("carbon_HL", "carbon_LL", "carbon_IO", "carbon_DO")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    facet_wrap("variable") + 
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```


## Terrestiral Carbon 

```{r}
percent_change_data %>%
    dplyr::filter(variable %in% c("npp")) %>% 
    ggplot(aes(year, percent, color = scenario)) + 
    geom_hline(yintercept = 10, color = "grey", size = 1) + 
    geom_hline(yintercept = -10, color = "grey", size = 1) + 
    geom_line() + 
    facet_wrap("variable") + 
    labs(caption = "grey lines at -10 & 10%") + 
    labs(x = NULL, y = "%")
```
